Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2023-11-14 index.Rmd
email

Academic email: andres.karjus --at-- tlu.ee <br>
Business and workshop inquiries: kindly contact via the <a href=https://datafigure.eu/contact.html</a> email  
<br>
<br>
Twitter / X: <a href=https://twitter.com/AndresKarjus>twitter.com/AndresKarjus</a> <br>
Bluesky: <a href=https://bsky.app/profile/andreskarjus.bsky.social>bsky.app/profile/andreskarjus.bsky.social</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">www.linkedin.com/in/andreskarjus/</a> <br> 
</div>

>>>>

Academic email: andres.karjus --at-- tlu.ee <br>
Business and workshop inquiries: kindly contact via the Datafigure <a href=https://datafigure.eu/contact.html>email</a>   
<br>
<br>
Twitter / X: <a href=https://twitter.com/AndresKarjus>twitter.com/AndresKarjus</a> <br>
Bluesky: <a href=https://bsky.app/profile/andreskarjus.bsky.social>bsky.app/profile/andreskarjus.bsky.social</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">www.linkedin.com/in/andreskarjus/</a> <br> 
</div>
